The Revisited Hidden Weight Bit Function

### 2025-08-27 paper.tex
Minors

\newcommand{\AI}{\mathsf{AI}}
\newcommand{\Bfn}[1]{\mathcal{B}_{#1}}
\newcommand{\BN}{\mathcal{B}_n}
\newcommand{\C}{\mathbb{C}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\degg}{\mathsf{deg}}
\newcommand{\dis}{\mathsf{c_1}}
\newcommand{\Dkna}[3]{\mathsf{D}_{#2,#1}(a)}
\newcommand{\Dtkna}[4]{\mathsf{D}_{#1,#2,#3}(#4)}
\newcommand{\ee}{\mathrm e\mkern1mu}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\FAI}{\mathsf{FAI}}
\newcommand{\hd}{\mathsf{d_H}}
\newcommand{\hwbf}{\ensuremath{\mathsf{HWBF}}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\ii}{\mathrm i\mkern1mu}
\newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
\newcommand{\myurl}[1]{\footnote{\texttt{\url{#1}}}}
\newcommand{\NL}{\mathsf{NL}}
\newcommand{\phikn}[2]{\varphi_{#1,#2}}
\newcommand{\w}{\mathsf{w_H}}
\newcommand{\WD}[2]{\mathcal{WD}^{#1}_{#2}}
\newcommand{\wt}[1]{\mathcal W_{#1}} 
\newcommand{\wtk}[2]{\mathcal{W}_{#1,#2}}
\newcommand{\Z}{\mathbb{Z}}

@@

@@

    \begin{proof}
    	We use Proposition~\ref{prop:WT}, applying Remark~\ref{rmk:dependence_Dkna} and that $\pi^{-1}(0_n)=0_n$:
    	\begin{align*}
    		\wt{f}(0_n)&=1+\sum_{k=1}^n\Dkna{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
    		&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+\sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}.
    	\end{align*}
    	Using the recursive relation from Proposition~\ref{prop:recursiveDkna}, we obtain:
    	\begin{align*}
    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\Dkna{n-2}{k}{1,1,0,1,\ldots,0,1}\\
    		&\qquad+\Dkna{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
    	\end{align*}
    	By reapplying this $n/2-1$ times, we obtain:
    	\begin{align*}
    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dkna{2}{k-2i}{1,1}\\
    		&=\binom{n/2-1}{k/2} \Dkna{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dkna{2}{1}{1,1}\\
    		&\qquad+ \binom{n/2-1}{k/2-1} \Dkna{2}{2}{1,1}\\
    		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
    	\end{align*}
    	We similarly get:
        \[
            \Dkna{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
        \]
        Then, combining both, we obtain:
    	\begin{align*}
    		\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+ \sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}\\
    		&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&\qquad+\sum_{k=n/2+1}^{n}\left(\binom{n/2-1}{k/2}+2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&\qquad+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
    		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right).
    	\end{align*}
    	Therefore, we get $\wt{f}(0_n)=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right)$. The final result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
    \end{proof}

@@

    \bibliographystyle{splncs04}
    {\small\bibliography{biblio}}

@@

        Similarly to the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{t,a}(z)|$ on $\dis=\{ z \in \C: |z|=1  \}$ for $a\in\F_2^n$, and this will then be an upper bound on $|\Dtkna tkna|$ for every $k\in[0,n]$. We write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$, and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}. To find a bound for $|P_{t,a}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{t,a}(z)|$. Moving through all $a\in\F_2^n$ is equivalent to moving through all tuples $(p,q,r;u,v)$ of non-negative integers which satisfy $p+q+r=t$ and $u+v=n-2t$. It follows from Lemma~\ref{lemma:maximizing_args} that it is enough to consider only the cases for which only one of $p,q,r$ is non-zero, and for which only one of $u,v$ is non-zero. This leaves us with the following cases to consider for $(p,q,r;u,v)$:
        \begin{gather*}
            (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
            (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
        \end{gather*}
        Since simultaneously replacing $(p,q)$ by $(q,p)$ and $(u,v)$ by $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{t,a}(z)$ and therefore does not change the maximum of $|P_{t,a}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
        \[
            (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
        \]

        Let us start by bounding $|P_{t,a}(z)|$ on $\dis$ in the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
        \[
            P_{t,a}(z)=\left((-z^2+2z+1)^{\lambda}(1+z)^{1-2\lambda}\right)^n.
        \]
        Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
        \begin{align*}
            |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
            &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
            &=6-2\cos (2\alpha),
        \end{align*}
        where the last equality uses that $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
    	\begin{align*}
    		P_{t,a}(z)|^2&=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n\\
    		&=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
    	\end{align*}
        The goal will be to prove that the maximum of the function $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$. Note that $g$ is an even function, so it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.

        \begin{figure}
        	\centering
        	\includegraphics[width=10cm]{graphs/family_curves_g.pdf}
            \vspace{-4mm}
        	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (the curve with the highest value at $\alpha=0$) to $i=24$ (the curve with the lowest value at $\alpha=0$).}
        	\label{fig:family_curves_g}
        \end{figure}

@@

        Therefore, in case $\lambda<1/6$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required. For $\lambda=1/6$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$. In case $\lambda>1/6$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$. For this $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=4\lambda^2-8\lambda+3-4\lambda\sqrt{\lambda^2-4\lambda+2}$. If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
        \[
            g(\alpha_0)=\frac{\left(-8\lambda^2+16\lambda+8\lambda\sqrt{\lambda^2-4\lambda+2}\right)^{\lambda}}{\left(2-2\lambda+2\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}=2^{2\mu}.
        \]
        With this, we have covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely. Similarly, it can be proven that $|P_{t,a}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$. For $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ since $0\leq h(\alpha)\leq g(\alpha)$.
    \end{proof}
\end{document}

>>>>

\newcommand{\AI}{\mathsf{AI}}
\newcommand{\Bfn}[1]{\mathcal{B}_{#1}}
\newcommand{\BN}{\mathcal{B}_n}
\newcommand{\C}{\mathbb{C}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\degg}{\mathsf{deg}}
\newcommand{\dis}{\mathsf{c_1}}
\newcommand{\Dkna}[3]{\mathsf{D}_{#2,#1}(a)}
\newcommand{\Dtkna}[4]{\mathsf{D}_{#1,#2,#3}(#4)}
\newcommand{\ee}{\mathrm e\mkern1mu}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\FAI}{\mathsf{FAI}}
\newcommand{\hd}{\mathsf{d_H}}
\newcommand{\hwbf}{\textsf{HWBF}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\ii}{\mathrm i\mkern1mu}
\newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
\newcommand{\myurl}[1]{\footnote{\texttt{\url{#1}}}}
\newcommand{\NL}{\mathsf{NL}}
\newcommand{\phikn}[2]{\varphi_{#1,#2}}
\newcommand{\w}{\mathsf{w_H}}
\newcommand{\WD}[2]{\mathcal{WD}^{#1}_{#2}}
\newcommand{\wt}[1]{\mathcal W_{#1}} 
\newcommand{\wtk}[2]{\mathcal{W}_{#1,#2}}
\newcommand{\Z}{\mathbb{Z}}

@@

\bibliographystyle{splncs04}

@@

    \begin{proof}
    	We use Proposition~\ref{prop:WT}, applying Remark~\ref{rmk:dependence_Dkna} and that $\pi^{-1}(0_n)=0_n$:
    	\begin{align*}
    		\wt{f}(0_n)&=1+\sum_{k=1}^n\Dkna{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
    		&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+\sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}.
    	\end{align*}
    	Using the recursive relation from Proposition~\ref{prop:recursiveDkna}, we obtain:
    	\begin{align*}
    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\Dkna{n-2}{k}{1,1,0,1,\ldots,0,1}\\
    		&\qquad+\Dkna{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
    	\end{align*}
    	By reapplying this $n/2-1$ times, we obtain:
    	\begin{align*}
    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dkna{2}{k-2i}{1,1}\\
    		&=\binom{n/2-1}{k/2} \Dkna{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dkna{2}{1}{1,1}\\
    		&\qquad+ \binom{n/2-1}{k/2-1} \Dkna{2}{2}{1,1}\\
    		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
    	\end{align*}
    	We similarly get:
        \[
            \Dkna{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
        \]
        Then, combining both, we obtain:
    	\begin{align*}
    		\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+ \sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}\\
    		&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&\qquad+\sum_{k=n/2+1}^{n}\left(\binom{n/2-1}{k/2}+2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2}-\binom{n/2-1}{k/2-1}\right)\\
    		&\qquad+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
    		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
            &=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right).
    	\end{align*}
    	The result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
    \end{proof}

@@

@@

        Similarly to the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{t,a}(z)|$ on $\dis=\{ z \in \C: |z|=1  \}$ for $a\in\F_2^n$, and this will then be an upper bound on $|\Dtkna tkna|$ for every $k\in[0,n]$. We write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$, and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}. To find a bound for $|P_{t,a}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{t,a}(z)|$. Moving through all $a\in\F_2^n$ is equivalent to moving through all tuples $(p,q,r;u,v)$ of non-negative integers which satisfy $p+q+r=t$ and $u+v=n-2t$. It follows from Lemma~\ref{lemma:maximizing_args} that it is enough to consider only the cases for which only one of $p,q,r$ is non-zero, and for which only one of $u,v$ is non-zero. This leaves us with the following cases to consider for $(p,q,r;u,v)$:
        \begin{gather*}
            (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
            (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
        \end{gather*}
        Since simultaneously replacing $(p,q)$ by $(q,p)$ and $(u,v)$ by $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{t,a}(z)$ and therefore does not change the maximum of $|P_{t,a}(z)|$ on $\dis$, we can restrict ourselves to the following tuples for $(p,q,r;u,v)$:
        \[
            (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
        \]

        Let us start by bounding $|P_{t,a}(z)|$ on $\dis$ in the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
        \[
            P_{t,a}(z)=\left((-z^2+2z+1)^{\lambda}(1+z)^{1-2\lambda}\right)^n.
        \]
        Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
        \[
            |-z^2+2z+1|^2=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right).
        \]
        Expanding yields $|-z^2+2z+1|^2=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}=6-2\cos(2\alpha)$ because $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
    	\begin{align*}
    		P_{t,a}(z)|^2&=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n\\
    		&=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
    	\end{align*}
        The goal will be to prove that the maximum of the function $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$. Note that $g$ is an even function, so it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.

        \begin{figure}
        	\centering
        	\includegraphics[width=10cm]{graphs/family_curves_g.pdf}
        	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (the curve with the highest value at $\alpha=0$) to $i=24$ (the curve with the lowest value at $\alpha=0$).}
        	\label{fig:family_curves_g}
        \end{figure}

@@

        Therefore, in case $\lambda<1/6$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required. For $\lambda=1/6$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$. In case $\lambda>1/6$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$. For this $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=4\lambda^2-8\lambda+3-4\lambda\sqrt{\lambda^2-4\lambda+2}$. If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
        \[
            g(\alpha_0)=\frac{\left(-8\lambda^2+16\lambda+8\lambda\sqrt{\lambda^2-4\lambda+2}\right)^{\lambda}}{\left(2-2\lambda+2\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}=2^{2\mu}.
        \]
        With this, we have covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely. Similarly, it can be proven that $|P_{t,a}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$. For $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ since $0\leq h(\alpha)\leq g(\alpha)$.
    \end{proof}

    \bibliography{biblio}
\end{document}
